Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-07 main.tex
Another thought

\bcp{I'm having some trouble here.  Two main problems so far:
  \begin{itemize}
  \item Since the ``high part'' of the world keeps getting extended as
  tainted data gets written here and there, the only way for something
  ``bad'' to happen is for high/tainted data to get written to someplace
  that was designated as an ``output''.  We don't currently have any way of
  making such a designation.
  \item Even after adding a separate IFC-like label for ``internal'' cells
  (that are not scrambled but also not outputs), I'm not seeing clearly how
  to formulate taint checking as an NI-like property.  Need to think about
  it some more.
  \end{itemize}
}

>>>>

\bcp{I'm having some trouble here.  Two main problems so far:
  \begin{itemize}
  \item Since the ``high part'' of the world keeps getting extended as
  tainted data gets written here and there, the only way for something
  ``bad'' to happen is for high/tainted data to get written to someplace
  that was designated as an ``output''.  We don't currently have any way of
  making such a designation.

  I guess we can add a ``middle'' classification level, and doing that here
  seems to make pretty good sense, but it's hard to justify adding it to the
  general definition of NI.  :-(
  \end{itemize}
}
